\documentclass[11pt]{article}
\usepackage[T1]{fontenc}
\usepackage{inter}
\renewcommand*\familydefault{\sfdefault}
\usepackage[dvipsnames]{xcolor}
\definecolor{gr}{RGB}{136,0,29}
\newcommand\ruleafter[1]{#1~\xrfill[.5ex]{1pt}[gr]}
\usepackage{geometry}
\geometry{
    a4paper,
    top=1.8cm,
    bottom=1in,
    left=2.5cm,
    right=2.5cm
}
\setcounter{secnumdepth}{0}
\pdfgentounicode=1
\usepackage{enumitem}
\setlist[itemize]{
    noitemsep,
    left=2em
}
\setlist[description]{itemsep=0pt}
\setlist[enumerate]{align=left}
\colorlet{icnclr}{gray}
\usepackage{titlesec}
\titlespacing{\subsection}{0pt}{*0}{*0}
\titlespacing{\subsubsection}{0pt}{*0}{*0}
\titleformat{\section}{\color{gr}\large\fontseries{black}\selectfont\uppercase}{}{}{\ruleafter}[\global\RemVStrue]
\titleformat{\subsection}{\fontseries{bold}\selectfont}{}{}{\rvs}
\titleformat{\subsubsection}{\color{gray}\fontseries{bold}\selectfont}{}{}{}
\usepackage{xhfill}
\newif\ifRemVS
\newcommand{\rvs}{
    \ifRemVS
    \vspace{-1.5ex}
    \fi
    \global\RemVSfalse
}
\usepackage{fontawesome5}
\usepackage[bookmarks=false]{hyperref}
\hypersetup{
    colorlinks=true,
    urlcolor=Sepia,
    pdftitle={Ho-min Park - CV (Education Focus)},
}
\usepackage[page]{totalcount}
\usepackage{fancyhdr}
\pagestyle{fancy}
\renewcommand{\headrulewidth}{0pt}
\fancyhf{}
\usepackage{amsmath}
\usepackage{amsfonts}
\begin{document}
\definecolor{gr}{RGB}{136,0,29}
\titleformat{\section}{\color{gr}\large\fontseries{black}\selectfont\uppercase}{}{}{\ruleafter}[\global\RemVStrue]
%== HEADER ==%
\begin{center}
    {\fontsize{28}{28}\selectfont Ho-min Park} \\
    \bigskip
    {\color{icnclr}\faMapMarker} Incheon, South Korea \quad
    {\color{icnclr}\faEnvelope[regular]} \href{mailto:homin.park@ghent.ac.kr}{homin.park@ghent.ac.kr}, \href{mailto:powersimmani@gmail.com}{powersimmani@gmail.com} \quad{\color{icnclr}\faIcon{mobile-alt}} \href{tel:+82-10-4731+3162}{+82-10-4731-3162}
    \\
    {\color{icnclr}\faGithub} \href{https://github.com/powersimmani}{github.com/powersimmani}
    \quad{\color{icnclr}\faOrcid} \href{https://orcid.org/0000-0001-9937-8617}{0000-0001-9937-8617}
    \quad{\color{icnclr}\faLinkedin} \href{https://www.linkedin.com/in/park-ho-min-b46658a6}{LinkedIn}
    \quad{\color{icnclr}\faGlobe} \href{https://powersimmani.github.io}{powersimmani.github.io}
\end{center}

\section{About me}
Computer Science Engineering PhD with deep expertise in machine learning, spanning from foundational concepts to state-of-the-art architectures including CNNs, Transformers, GANs, and Diffusion models. Designed and delivered a comprehensive 20-lecture ML curriculum over 4 years through the AI Vacation School (AIVS) program, creating original educational materials with lecture slides, hands-on Colab notebooks, and step-by-step Excel worksheets for algorithm understanding. Experienced in evaluating and iteratively improving ML educational content based on learner feedback and evolving research trends. Authored 7 peer-reviewed publications applying ML across diverse domains (medical imaging, bioinformatics, affective computing, environmental science), providing broad perspective for assessing ML lecture materials across application areas.

\section{ML Education \& Curriculum Design}
\subsection{AI Vacation School (AIVS) -- Founder \& Lead Instructor\hfill \normalfont 2021 - 2025}
\subsubsection{Ghent University Global Campus}
\begin{itemize}
    \item[\checkmark] Founded and led a volunteer-driven ML bootcamp (100+ hours per session) for undergraduate students over 7 sessions across 4 years, iteratively refining content based on learner feedback and emerging research trends. [\href{https://github.com/powersimmani/AIVS}{Introduction}, \href{https://powersimmani.github.io/AIVS_Lecture_Slides/}{Lecture Slides}]
    \item[\checkmark] Designed a 20-lecture curriculum spanning the full ML pipeline: regression, MLPs, CNNs, RNNs, Transformers, LLMs, GANs, Diffusion models, unsupervised learning, and XAI (SHAP).
    \item[\checkmark] Created three types of original materials per topic: presentation slides, Google Colab notebooks, and Excel worksheets for step-by-step manual computation of ML algorithms.
    \item[\checkmark] Developed a three-stage pedagogical framework (pre-session self-study, on-site intensive training, independent research project) with level-based progression (Beginner, Advanced, Advanced Plus).
    \item[\checkmark] Mentored over 10 entry-level AI researchers with follow-up seminars, portfolio development guidance, and recommendation letters.
\end{itemize}

\section{Education}
\subsection{Ph.D. in Computer Science Engineering\hfill \normalfont 2018 - 2025}
\subsubsection{Ghent University, Belgium}
\begin{itemize}
    \item[\checkmark] Dissertation: ``Advancing Detection through Deep Learning for Industrial, Environmental, and Health Applications''
    \item[\checkmark] Advisors: Prof. Wesley De Neve, Prof. Arnout Van Messem
\end{itemize}

\subsection{M.S. in Computer Engineering\hfill \normalfont 2016 - 2018}
\subsubsection{Ajou University, Suwon, South Korea}
\begin{itemize}
    \item[\checkmark] Thesis: ``Cited count prediction modeling from large citation network"
\end{itemize}

\subsection{B.S. in Computer Science and Engineering\hfill \normalfont 2010 - 2016}
\subsubsection{Ajou University, Suwon, South Korea}
\begin{itemize}
    \item[\checkmark] Major in Computer Science and Engineering
\end{itemize}

\section{Skills}
\subsection{ML \& AI Expertise}
\begin{itemize}
    \item[\checkmark] \textit{Architectures:} CNN, RNN, LSTM, GRU, Transformer, GAN, Diffusion Models, Multi-layer Perceptrons
    \item[\checkmark] \textit{Techniques:} Supervised/Unsupervised Learning, Transfer Learning, Feature Engineering, Model Explainability (SHAP, CAM)
    \item[\checkmark] \textit{Domains:} Medical Imaging (MRI), Bioinformatics (CRISPR-Cas), Affective Computing, Environmental Science, Industrial Systems
\end{itemize}
\subsection{Educational Tools \& Platforms}
\begin{itemize}
    \item[\checkmark] \textit{Curriculum Design:} 4 years of ML curriculum development, iterative improvement based on learning outcomes
    \item[\checkmark] \textit{Teaching Platforms:} Google Colab, Jupyter Notebook, GitHub Pages, reveal.js-based slide systems
    \item[\checkmark] \textit{MLOps \& Development:} PyTorch, PyTorch Lightning, Weights and Biases (WandB), Python
\end{itemize}
\subsection{Languages}
\subsubsection{Korean}
\begin{itemize}
    \item[\checkmark] Native speaker.
\end{itemize}
\subsubsection{English}
\begin{itemize}
    \item[\checkmark] \textit{Writing:} Demonstrated through technical documentation and research publications.
    \item[\checkmark] \textit{Reading:} Evident through the comprehension of technical and academic literature.
    \item[\checkmark] \textit{Speaking and Listening:} Applied in collaborative environments with international teams.
\end{itemize}

\section{Publications}
\subsection{Journal Articles}
\begin{itemize}
    \item[\checkmark] Park, H., Kim, G., Oh, J., Van Messem, A., \& De Neve, W. (2024) Interpreting stress detection models using SHAP and attention for MuSe-Stress 2022. \textit{IEEE Transactions on Affective Computing}, \textbf{15}(01): 1-17. DOI: \href{https://doi.org/10.1109/TAFFC.2024.3488112}{10.1109/TAFFC.2024.3488112}.
    \item[\checkmark] Park, H., Won, J., Park, Y., Anzaku, E. T., Vankerschaver, J., Van Messem, A., De Neve, W., \& Shim, H. (2023) CRISPR-Cas-Docker: Web-based in silico docking and machine learning-based classification of crRNAs with Cas proteins. \textit{BMC Bioinformatics}, \textbf{24}(1): 167. Springer.
    \item[\checkmark] Park, H., Park, Y., Berani, U., Bang, E., Vankerschaver, J., Van Messem, A., De Neve, W., \& Shim, H. (2022) In silico optimization of RNA-protein interactions for CRISPR-Cas13-based antimicrobials. \textit{Biology Direct}, \textbf{17}(1). DOI: \href{https://doi.org/10.1186/s13062-022-00339-5}{10.1186/s13062-022-00339-5}.
    \item[\checkmark] Park, H., Park, Y., Vankerschaver, J., Van Messem, A., De Neve, W., \& Shim, H. (2022) Rethinking protein drug design with highly accurate structure prediction of anti-CRISPR proteins. \textit{Pharmaceuticals}, \textbf{15}(3). DOI: \href{https://doi.org/10.3390/ph15030310}{10.3390/ph15030310}.
    \item[\checkmark] Park, H., Park, S., de Guzman, M. K., Baek, J. Y., Cirkovic Velickovic, T., Van Messem, A., \& De Neve, W. (2022) MP-Net: Deep learning-based segmentation for fluorescence microscopy images of microplastics isolated from clams. \textit{PLoS ONE}, \textbf{17}(6): e0269449. DOI: \href{https://doi.org/10.1371/journal.pone.0269449}{10.1371/journal.pone.0269449}.
\end{itemize}
\subsection{Conference Articles}
\begin{itemize}
    \item[\checkmark] Nguyen, K. T., Park, H., Oh, G., Vankerschaver, J., \& De Neve, W. (2025) Towards Improved Cervical Cancer Screening: Vision Transformer-Based Classification and Interpretability. \textit{IEEE 22nd International Symposium on Biomedical Imaging (ISBI)}.
    \item[\checkmark] Park, H., Yun, I., Kim, M., Nguyen, K. T., Van Messem, A., \& De Neve, W. (2024) Interpretable Rotator Cuff Tear Diagnosis Using MRI Slides with CAMscore and SHAP. \textit{Medical Imaging 2024: Computer-Aided Diagnosis}, Vol. 12927: 683-693. SPIE.
    \item[\checkmark] Singh, A. K., Kim, G., Kim, J., Park, H., Choi, B. J., \& De Neve, W. (2024) Exploring Multimodal Approaches and Fusion Methods for CEO Social Attribute Prediction in 2024 MuSe-Perception. \textit{Proceedings of the 5th on Multimodal Sentiment Analysis Challenge and Workshop: Social Perception and Humor}, 36–44. Melbourne VIC, Australia: ACM. DOI: \href{https://doi.org/10.1145/3689062.3689081}{10.1145/3689062.3689081}.
    \item[\checkmark] Park, H., Kim, G., Van Messem, A., \& De Neve, W. (2023) MuSe-Personalization 2023: Feature engineering, hyperparameter optimization, and transformer-encoder re-discovery. \textit{Proceedings of the 4th Multimodal Sentiment Analysis Challenge and Workshop: Mimicked Emotions, Humour and Personalisation}, 89–97. Ottawa ON, Canada: ACM. DOI: \href{https://doi.org/10.1145/3606039.3613104}{10.1145/3606039.3613104}.
    \item[\checkmark] Park, H., Yun, I., Kumar, A., Singh, A. K., Choi, B. J., Singh, D., \& De Neve, W. (2022) Towards multimodal prediction of time-continuous emotion using pose feature engineering and a transformer encoder. \textit{Proceedings of the 3rd International on Multimodal Sentiment Analysis Workshop and Challenge}, 47–54. DOI: \href{https://doi.org/10.1145/3551876.3554807}{10.1145/3551876.3554807}.
    \item[\checkmark] Baek, J. Y., de Guzman, M. K., Park, H., Park, S., Shin, B., Cirkovic Velickovic, T., Van Messem, A., \& De Neve, W. (2021) Developing a segmentation model for microscopic images of microplastics isolated from clams. \textit{Pattern Recognition, ICPR International Workshops and Challenges, Proceedings, Part VI}, 12666: 86–97. Cham: Springer. DOI: \href{https://doi.org/10.1007/978-3-030-68780-9_9}{10.1007/978-3-030-68780-9\_9}.
    \item[\checkmark] Park, H., Kang, B., Van Messem, A., \& De Neve, W. (2021) 3-D deep learning-based item classification for belt conveyors targeting packaging and logistics. \textit{Pattern Recognition, ICPR International Workshops and Challenges, Proceedings, Part VI}, 12666: 578–591. Cham: Springer. DOI: \href{https://doi.org/10.1007/978-3-030-68799-1_42}{10.1007/978-3-030-68799-1\_42}.
    \item[\checkmark] Kang, H., Park, H., Ahn, Y., Van Messem, A., \& De Neve, W. (2021) Towards a quantitative analysis of class activation mapping for deep learning-based computer-aided diagnosis. \textit{Medical Imaging 2021: Image Perception, Observer Performance, and Technology Assessment, Vol. 11599}, SPIE. DOI: \href{https://doi.org/10.1117/12.2580819}{10.1117/12.2580819}.
    \item[\checkmark] Park, H., Van Messem, A., \& De Neve, W. (2020) Item measurement for logistics-oriented belt conveyor systems using a scenario-driven approach and automata-based control design. \textit{IEEE 7th International Conference on Industrial Engineering and Applications (ICIEA 2020)}, Bangkok and Phuket.
    \item[\checkmark] Park, H., Van Messem, A., \& De Neve, W. (2019) Box-Scan: An efficient and effective algorithm for box dimension measurement in conveyor systems using a single RGB-D camera. \textit{The 7th IIAE International Conference on Industrial Application Engineering}, Kitakyushu, Japan.
\end{itemize}

\section{Funded Projects}
\subsection{Depression Diagnosis \& Drug Adherence Research (2022 - 2025)}
\begin{itemize}
    \item[\checkmark] Developed advanced models for the MuSe-Stress and MuSe-Personalization challenges.
    \item[\checkmark] Implemented Transformer Encoders and novel feature engineering techniques.
    \item[\checkmark] Achieved 2nd place in MuSe-Personalisation 2023 and 3rd place in MuSe-Stress 2022.
    \item[\checkmark] Contributed to the field of affective computing with interpretable AI models.
    \item[\checkmark] \textbf{Funding:} National Research Foundation of Korea (Grant No.: NRF-2020K1A3A1A68093469), Department of Biotechnology in India (Grant No.: DBT/IC-12031(22)-ICD-DBT), and Ghent University Global Campus
\end{itemize}

\subsection{Environmental Monitoring Project (2020 - 2023)}
\begin{itemize}
    \item[\checkmark] Led development of MP-Net, an AI system for automated microplastics detection
    \item[\checkmark] Designed and implemented a microplastics annotation tool for dataset creation
    \item[\checkmark] Managed collaboration between environmental scientists and AI engineers
    \item[\checkmark] \textbf{Funding:} Special Research Fund of Ghent University (Grant No.: 01N01718) and Ghent University Global Campus
\end{itemize}

\subsection{Smart Packaging System Development (2018 - 2021)}
\begin{itemize}
    \item[\checkmark] Developed and patented two AI-powered measurement systems for industrial conveyor belts
    \item[\checkmark] Led implementation of 3D deep learning-based item classification system
    \item[\checkmark] Designed integrated size and type monitoring system
    \item[\checkmark] Collaborated with industry partners to deploy solutions in real factory environments
    \item[\checkmark] \textbf{Funding:} Ministry of Trade, Industry, and Energy (MOTIE), Korea (Project No.: 10077285)
\end{itemize}

\section{Patents}
\begin{itemize}
    \item[\checkmark] Park, H., \& De Neve, W. (2020) An apparatus and method for measuring the size of high-speed objects and classifying their type on conveyors using light curtain sensors. Korean Intellectual Property Office. Application no.: 10-2020-0045098, Registration no.: 10-2273758.
    \item[\checkmark] Park, H., \& De Neve, W. (2018) Apparatus and method for measuring the size of high-speed boxes on conveyors using an RGB-D camera. Korean Intellectual Property Office. Application no.: 10-2018-0148118, Registration no.: 10-2066862.
\end{itemize}

\section{Awards \& Certifications}
\subsection{Awards}
\begin{itemize}
    \item[\checkmark] \textbf{Second Place}, MuSe-Personalisation Challenge 2023, awarded for multimodal sentiment analysis contributions.
    \item[\checkmark] \textbf{Third Place}, MuSe-Stress Challenge 2022, awarded for contributions to multimodal sentiment analysis.
    \item[\checkmark] \textbf{Best Presentation Award}, International Conference on Industrial Application Engineering (IIAE), 2019, for effective research communication and presentation.
\end{itemize}

\subsection{Certifications}
\begin{itemize}
    \item[\checkmark] \textbf{TOEIC} – Score: 860 points, Date: September 7, 2024
    \item[\checkmark] \textbf{OPIc} – Level: Intermediate High (IH), Date: September 17, 2024
    \item[\checkmark] \textbf{Information Processing Engineer} – Certification No.: 15202100118F, Date: July 31, 2015
    \item[\checkmark] \textbf{Information Processing Industrial Engineer} – Certification No.: 12642002187H, Date: November 30, 2012
    \item[\checkmark] \textbf{Information Equipment Operation Craftsman} – Certification No.: 06402100644N, Date: June 26, 2006
    \item[\checkmark] \textbf{Information Processing Craftsman} – Certification No.: 04402100928U, Date: June 21, 2004
\end{itemize}

\section{References}
\textcolor{Sepia}{References available upon request.}

\end{document}
